Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

When concurrent programs are written by developers, the manual memory management is extremely difficult and error-prone. When multiple threads access a common object, dangling pointers are a common scenario due to the incomplete information about ownership. Double-free bugs can occur just as frequently as the dangling pointers. Smart pointers are the defacto standard to avoid memory management issues in concurrent programs. These smart pointers do not guarantee complete garbage collection. The use of cyclic objects in the heap memory requires extreme care in a manually managed concurrent program. It is carefully avoided by all programmers usually to make the program memory leak free. The above reasons explain how difficult the automatic memory management in the concurrent programming environment is and the necessity for high-quality automatic memory management in concurrent programming environments.

>>>>

When concurrent programs are written by developers, manual memory management is extremely difficult and error-prone. When multiple threads access a common object, dangling pointers are a common scenario due to the incomplete information about ownership. Double-free bugs can occur just as frequently as the dangling pointers. Smart pointers are the defacto standard to avoid memory management issues in concurrent programs. These smart pointers do not guarantee complete garbage collection. The use of cyclic objects in heap memory requires extreme care in a manually managed concurrent program. It is carefully avoided by all programmers usually to make the program memory leak free. The above reasons explain difficulties of automatic memory management in the concurrent programming environment and the necessity for high-quality automatic memory management in concurrent programming environments.
